---
title: "Homework4"
author: "Anbin Rhee"
date: "10/20/2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Problem 1
If I need a bit more work with the tidyverse, I will check out Rstudio.cloud Primer titled “Tidy your data”.

# Problem 2
I used R Markdown file for this homework.

# Problem 3

## Part A
```{r Part A 1}
library(dplyr)
library(tidyr)
library(reshape)
PartA <- read.delim("https://www2.isye.gatech.edu/~jeffwu/wuhamadabook/data/ThicknessGauge.dat",header = FALSE, skip = 2, sep=" ")
colnames(PartA) <- c("part","1.1","1.2","2.1","2.2","3.1","3.2")
PartA <- melt(PartA, id.vars = "part")
PartA <- separate(data = PartA, col = 'variable',into = c("operator", "measurement"))
```

I imported the data and renamed the columns as "1.1", "1.2", "2.1", "2.2", "3.1", and "3.2". 
Then, I rearranged the data in order to the observations to be distinguished and separated the observations by operator and measurement.

```{r Part A 3}
PartA$part <- factor(PartA$part)
PartA$operator <- factor(PartA$operator)
PartA$measurement <- factor(PartA$measurement)
summary(PartA)
knitr::kable(PartA, caption = "Measurements of the part’s wall thickness")
PartAplot <- aggregate(x = PartA$value, by = list(PartA$part, PartA$operator), FUN = mean)
PartAplot['difference'] <- PartAplot$x - mean(PartAplot$x)
par(xpd=TRUE)
barplot(difference ~ Group.2 + Group.1,
        data = PartAplot,
        beside = TRUE,
        xlab = "Part",
        ylab = "Difference from the mean value of measurement",
        col = c("red", "blue", "purple"),
        ylim = c(-0.005,0.003),
        border = NA)
legend("bottomright", c("Operator 1", "Operator 2","Operator 3"),
       fill = c("red", "blue", "purple"), border = NA)
```

I showed the data as table form and drew a plot which shows the difference from the mean value of measurements. 

## Part B
```{r Part B 1}
PartB <- read.delim("https://www2.isye.gatech.edu/~jeffwu/wuhamadabook/data/BrainandBodyWeight.dat", header = FALSE, skip = 1, sep = " ")

# rename the columns
colnames(PartB) <- rep(c("BodyWeight", "BrainWeight"), 3)
# rearrange data frame to 2 columns
PartB <- rbind(PartB[,1:2], PartB[,3:4], PartB[1:20,5:6])
```

I imported the data of Part B and renamed the columns as "Body Weight" and "Brain Weight". Then, I rearranged the data.

```{r Part B 2}
summary(PartB)
knitr::kable(PartB, caption = "Body and brain weight")
# scatter plot and fitted simple linear model
plot(x = PartB$BodyWeight, y = PartB$BrainWeight,
     col = "red", pch = 16,
     xlab = 'Weight of body (kg)',
     ylab = 'Weight of brain (g)')
abline(lm(BrainWeight ~ BodyWeight, PartB),
       col = "green")
legend(x = "bottomright", legend = c("Raw data", "Fitted line"),
       col = c("red","green"), lty = c(0,1), pch = c(16,NA))
```

The summary of the data is presented in the table and the scatter plot between Body Weight and Brain Weight is also presented.  

## Part C
```{r Part C 1}
library(data.table)
PartC <- read.delim("https://www2.isye.gatech.edu/~jeffwu/wuhamadabook/data/LongJumpData.dat",header = FALSE, skip = 1, sep = " ")
colnames(PartC) <- rep(c("year", "long jump"), 4)
PartC <- rbind(PartC[,1:2], PartC[,3:4], PartC[,5:6], PartC[1:4, 7:8])
```

I imported data of Part C and renamed the columns as "year" and "long jump". 

```{r Part C 2}
PartC$year <- PartC$year + 1900
# show the table of data (first 6 observations)
knitr::kable(PartC, caption = "Gold Medal performance for Olympic Men’s Long Jump")
summary(PartC)
# scatter plot and fitted simple linear model
plot(PartC, col = "purple", lwd = 1,
     type = 'l',
     xlab = 'Year',
     ylab = 'Gold Medal performance for Men’s Long Jump (inch)')
```

The summary of the data of Part C is presented in table above. I also drew a scatter plot between year and gold medal performance for men's long jump.

## Part D

```{r Part Dn1}
PartD <- fread("https://www2.isye.gatech.edu/~jeffwu/wuhamadabook/data/tomato.dat",header = FALSE, skip = 0, sep = " ", sep2 = ",")
colnames(PartD) <- c("category", "10000", "20000", "30000")
PartD <- separate(data = PartD, col = '10000',into = c("10000.1", "10000.2", "10000.3"),
               remove = TRUE, sep = ',')
PartD <- separate(data = PartD, col = '20000',into = c("20000.1", "20000.2", "20000.3"),
               remove = TRUE, sep = ',')
PartD <- separate(data = PartD, col = '30000',into = c("30000.1", "30000.2", "30000.3"),
               remove = TRUE, sep = ',')
```

I imported the data in Part D and renamed the columns as "category", "10000", "20000", and "30000". Then, separated the columns by three.

```{r Part D 2}
PartD <- melt(PartD, id.vars = "category")
# separate columns to Planting Density and measurement
PartD <- separate(data = PartD, col = 'variable',
               into = c("PlantingDensity", "measurement"),remove = TRUE)
PartD$category <- factor(PartD$category)
PartD$PlantingDensity <- factor(PartD$PlantingDensity)
PartD$measurement <- factor(PartD$measurement)
PartD$value <- as.numeric(PartD$value)
knitr::kable(head(PartD), caption = "Measurements of tomato yield")
knitr::kable(summary(PartD), caption="Summary of variables")
PartDplot <- aggregate(x = PartD$value, by = list(PartD$category, PartD$PlantingDensity), FUN = mean)
# plot the yield by category and Planting Density
barplot(x ~ Group.1 + Group.2,
        data = PartDplot,
        beside = TRUE,
        col = c("orange", "blue"),
        xlab = "Planting Density",
        ylab = "Mean value of measurements for Yield",
        ylim = c(0,30),
        border = NA)
legend("top", c("Ife 1", "Pusa Early Dwarf"),
       fill = c("orange", "blue"),
       border = NA, horiz = TRUE)
```

I showed the summary of the data by table and drew a plot which shows the mean value of measurements for tomato yield.


## Part E

```{r message = FALSE, warning = FALSE, fig.cap = "Larvae counts in different blocks"}
library(ggplot2)
PartE <- read.delim("https://www2.isye.gatech.edu/~jeffwu/wuhamadabook/data/LarvaeControl.dat",header = FALSE, skip = 3, sep = " ")
PartE <- PartE[,colSums(is.na(PartE))<nrow(PartE)]
colnames(PartE) <- c("Block","Age1.Treatment1","Age1.Treatment2","Age1.Treatment3","Age1.Treatment4","Age1.Treatment5","Age2.Treatment1","Age2.Treatment2","Age2.Treatment3","Age2.Treatment4","Age2.Treatment5")
PartE <- melt(as.data.table(PartE), id.vars = "Block")
PartE <- separate(data = PartE, col = 'variable', into = c("age", "treatment"), remove = TRUE)
PartE$Block <- factor(PartE$Block)
PartE$age <- factor(PartE$age)
PartE$treatment <- factor(PartE$treatment)
knitr::kable(PartE, caption = "Larvae counts at two ages")
knitr::kable(summary(PartE), caption="Summary of variables")
ggplot(PartE, aes(y = value, x = Block, 
               color = treatment,
               shape = age))+
  geom_point(size = 4)+
  ylab("Larvae counts")
```

I imported the data of Part E and renamed the columns as "Block", "Age1.Treatment1", "Age1.Treatment2", "Age1.Treatment3", "Age1.Treatment4", "Age1.Treatment5", "Age2.Treatment1", "Age2.Treatment2", "Age2.Treatment3", "Age2.Treatment4", "Age2.Treatment5".
Also the summaries of the data are presented in tables above and drew a plot between Block and Larvae counts.

# Problem 5
I knitted this document to pdf and pushed to GitHub.


